Application of the least-squares method to the multiscale transport equation in porous media

### 2011-03-21 MSTE_methodology.tex
submitted version

\newcommand{\TODO}[1]{\textcolor{blue}{TODO: #1} \\}
\newcommand{\Fede}[1]{\textcolor{green}{Fede: #1} \\}
\newcommand{\Pablo}[1]{\textcolor{blue}{#1}}
\newcommand{\newf}[1]{\textcolor{green}{#1}}
\newcommand{\nof}[1]{\textcolor{cyan}{}}
%\newcommand{\nof}[1]{\textcolor{cyan}{{\sout{#1}}}}

@@

\abstract{
  This file is an example \LaTeX file for submission to CFD2011.  A
  limit of 10 pages applies.
}
\keywords{
  CFD, hydrodynamics, chemical reactors
}
\normalfont\normalsize

@@

\TODO{NOMENCLATURA!!}
\section{Introduction}
Theories for studying porous media were first formulated as early \newf{as }the end of the eighteen century\newf{,} after the volume fraction concept was introduced for describing mud. Half a century later\newf{,} one of the most basic law\newf{s} for saturated porous solids was established by Henry Darcy, i.e. the flow velocity of the liquid in a porous solid is proportional to the pressure gradient. Since then\newf{, increasingly} more complex theories for predicting the proportionality constant \newf{have arised}, incorporating the capillary force and considering deformable media with the definition of the consolidation problem \citep{Boer1992}.

@@

The multi-scale transport equation for porous media (MSTE) was proposed as an extension of approaches considering a finite number of groups as studied for example by \cite{Chen1989}, \cite{bouffard2001}. One internal coordinate was recently introduced \citep{DupuySchwarz} to the continuity problem for accounting the multi-scale transport of species and the scale-dependent physics. Furthermore, the MSTE defines a inter-pore redistribution function $h$ that makes the equation open and requires further research to find the most adequate closure or model.

@@

\newf{Several numerical methods have been developed for solving integro--differential equations in other areas of science. Examples are the neutron transport equation \cite{Duderstad1976} and the population balance equation \cite{Ramkrishna2000}. Most of these methods are designed to eliminate the integral terms from the equations.}
\newf{In recent years, the work by \cite{Dorao05a}, \cite{Patruno2010} and \cite{Sporleder2011} has shown the capability of the least-squares method (LSQ) to solve the integro-differential form of the equations directly. This spectral method is based on the idea that under certain conditions minimizing the residual of the equations defined with the numerical solution is equivalent to minimizing the error, i.e., the distance between the numerical solution and the exact solution \cite{Jiang1998}. This reformulation of the equations as a minimization problem is independent of the equations at hand, and therefore it allows for flexible and general--purpose programming. Besides, the method uses a measure of the residual as a built-in error estimator, and presents semi-analytical solutions, as the minimizing function is expanded in a family of basis functions. When combined with the finite or spectral element approach \cite{Gerritsma2010}, it is capable of solving large problems in arbitrary geometries, using unstructured meshes.}

@@

The term \nof{pore-size have}\newf{pore size has} been used loosely in the literature and needs to be addressed first. \newf{In our framework, it is a characteristic length that represents the pore scale. }\cite{Dullien} proposed \nof{to use}\newf{to define the pore size as} twice the hydraulic radius\nof{as a convenient definition but others might work as well in the present approach since what we are after is a characteristic length that will represent the pore scale}. \nof{Any of these choices requires a proper definition of a pore as a unity, for which any arbitrary definition of a portion of the void volume can chosen where a pore size can be measure (e.g. hydraulic radius) for each pore.}\newf{Other definitions may be used. Regardless of the choice, a consitent definition of a pore as a unity is required.} Most pore networks agree on the definition of these elementary units. Each pore will therefore have a volume. In the MSTE, all the void volume is assigned to pores, and the concept of throat \citep{oren2002, blunt2002, piri2005} is not needed\newf{. This is different to} \nof{making a difference with }some pore network strategies.

\Fede{Lo cambi\'e bastante porque no se entend\'ia, perd\'on. Si falta algo, ponga nom\'as...}
\Fede{Qu\'e es throat? Pore networks? Capaz alguna ref? Y si estas diferencias con otros m\'etodos establecidos las ponemos en la intro?}

\nof{Let's}\newf{Let us} define $\xi$ as the pore size, and $\epsilon(\xi)$ \newf{as the total volume of the pores} \nof{the summed volume for all the pores }of size $\xi$ per volume unit.
\nof{On average, the permeability will be different for each pore size as well, $k(\xi)$. A driven force will produce an advective velocity of the fluid at the scale $\xi$ denoted as $v(\xi)$, and the discharge (or slip velocity) for the same scale is $q(\xi)=\epsilon(\xi) v(\xi)$.}
\newf{We will indicate the permeability of a pore of size $\xi$ with $k(\xi)$, the advective velocity of the fluid at the scale $\xi$ as $v(\xi)$, and the discharge (or slip velocity) for the same scale as $q(\xi)=\epsilon(\xi) v(\xi)$}.

\Fede{De nuevo cambio, pero me pareci\'o que la intenci\'on era definir variables. Igual, no est\'a muy claro. Se nota que no estoy en tema. Pero m\'as all\'a de eso, te puedo preguntar si $\epsilon$ y $q$ son distribuciones o no (hasta ahora no, m\'as adelante s\'i), y a $\phi$ nunca la introduc\'is tampoco (s\'e que es el tracer, pero exactamente c\'omo se define??).}
\Fede{Capaz podr\'ias empezar definiendo $\phi$ y el problema f\'isico, poner la ecuaci\'on, describir los t\'erminos y las variables que aparecen claramente, y despu\'es las otras como $\epsilon$, que en la ecuaci\'on no figuran directamente... Te va as\'i? Esta secci\'on es cr\'itica, porque el modelo es muy muy poco conocido.}
\Fede{Dejo de corregir la secci\'on. Me gustar\'ia de ser posible que ac\'a hagas una intro al modelo general, y el 1D introducirlo despu\'es, como simplificaci\'on... }

\cite{DupuySchwarz} introduce the concept of the redistribution function $h(\xi_1 \rightarrow \xi_2)$ as the discharge from pores of size $\xi_1$ into pores of sizes $\xi_2$. This is a measure of the mixing between pores of different scales.

@@

The multi-scale transport for a tracer, specie $i$, in all the pores assuming one dimension ($z$) and steady state case can be written as \citep{DupuySchwarz}:

\begin{align}
q(z, \xi) \cdot \frac{\partial \phi_{i}(z, \xi)}{\partial z}  = 
 S_{i}(z, \xi) + \int [\phi_{i}(z, \hat \xi) - \phi_{i}(z, \xi)] h(z, \hat \xi \rightarrow \xi) d\hat \xi . 
\label{eq:ss2}
\end{align}

@@

\Fede{Te saqu\'e un aporte, no te ofendas :-)}

@@

\Pablo{Yo lo entiendo porque yo se LSQ (algo al menos)... pero no se como se explica mejor realmente... $\mathbf{f}$ es la solucion o es la aproximacion a la solucion? equacion 2 es inconsistente con el resto... o no? Es una muy poco feliz decision elegir el mismo symbolo para ambas, o no? Debido a que en nuestro problema la solucion es $\phi$ decidi hacer el cambio en la definicion del problema. Luego usamos $\mathbf{f}$ para la aprox solo.  Agregue un texto que capaz ayuda para aclarar ese punto.}
\Fede{Yo tampoco s\'e c\'omo explicarlo mejor, jeje. Es lo m\'as simplificado que puedo hacerlo, sin mandar fruta for export y sin ir en contra de los fundamentos matem\'aticos. Hice cambios basados en tus comentarios, y creo que ahora queda mejor. Pero sig aceptando sugerencias. No tengo forma f\'acil de explicar el espacio Y. Est\'a definido impl\'icitamente en el problema, es el espacio im\'agen del mapeo que hace el operador. }

@@

\Pablo{No he leido esta seccion todavia en mucho detalle. Pero parece estar bien. Si es la primera vez que se publica este tipo de informacion decime que agarro la lupa y la miro en mas detalle... se la podes dar a Hugo a ver si la entiende, jeje }
\Fede{Hugo se duerme en estas secciones. Dice que ya lo conoce, despu\'es me viene a preguntar 3 veces por semana cosas que explico justamente en estas secciones... Tengo un paper aceptado que muestra esto en casi igual :-)}
Using variational analysis, minimizing the functional $\mathcal{J}(\mathbf{f})$ is equivalent to finding $\mathbf{f} \in X(\Omega)$ such that:

@@

\Fede{Si el problema a resolver ya se introdujo en la segunda secci\'on, entonces esto de ac\'a puede ir a la secci\'on de implementaci\'on :-)}

@@

\begin{align}
\epsilon(\xi)=&A (\xi-\xi_0) (-\xi+\xi_f) \\
q({\xi}) =&V \epsilon(\xi) \xi^2\\
h(\hat \xi, \xi, z) =& q(\hat \xi) q(\xi)/L\\
\phi(\xi, z) =& 10 z (1-M Log({\xi}/R))\\
\nonumber S(\xi, z)=& 10 A V {\xi}^2 ({\xi}-\xi_0) (-{\xi}+\xi_f) \left(1-M \text{Log}\left[\frac{{\xi}}{R}\right]\right) +\\
\nonumber  &A^2 M V^2  (360 L)^{-1} {\xi}^2 ({\xi}-\xi_0) ({\xi}-\xi_f) z \times ... \\
\nonumber  &\big(-81 \xi_0^5+175 \xi_0^4 \xi_f-175 \xi_0 \xi_f^4+  ...\\
\nonumber &81 \xi_f^5+60 \xi_0^4 (3 \xi_0-5 \xi_f) \text{Log}\left[\frac{\xi_0}{{\xi}}\right]+ ...\\
& 60 (5 \xi_0-3 \xi_f) \xi_f^4 \text{Log}\left[\frac{\xi_f}{{\xi}}\right]\big)
\end{align}

\noindent \newf{with $A=\tfrac{1}{500}$, $V=0.001$, $M=1$ and pore scale limits $\xi_0=1$ and $\xi_f=10$ mm.}

@@

For completeness, the condition number versus the order of the approximation is shown in Figure \ref{fig:cond}. This number increases steeply with the order, reaching values over $10^12$. The condition number depends mostly on the fill-up of the matrix. The use of an element approach will reduce drastically this number. Larger models that use the MSTE are also expected to have lower condition numbers.

@@

Future work still remains on the area of finding the most adequate kernels that best represent different porous media. Mainly empirical studies of the redistribution function need to be done.
\Fede{Ahora me tengo que ir, pero hay que mejorar esta conclusi\'on}
\TODO{Conclusiones en serio?}
\TODO{Bibliograf\'ia!!}
%\abstract{
%  This file is an example \LaTeX file for submission to CFD2011.  A
%  limit of 10 pages applies.
%}
%\keywords{
%  CFD, hydrodynamics, chemical reactors
%}
%\normalfont\normalsize
%
%
%
%%\section{Nomenclature}
%A complete list of symbols used, with dimensions, is required.
%%the nomenclature needs to be entered into the file ExampleFile.nls
%\printnomenclature[0.7cm]  
%\vskip .1em
%
%
%\section{Introduction}
%The introduction goes here.
%
%
%\newpage
%
%
%
%\section{Model Description}
%You should give a thorough description of your model.
%\vspace{4cm}
%\subsection{Example of Subheading}
%Here is how to produce a numbered equation under a second level
%heading \cite{James1988}.
%\vspace{2cm}\\
%\emph{Continuity equation}
%\begin{equation}
%  \frac{\partial \rho_G}{\partial t}+\nabla\left(\rho_G\mathbf
%    u\right)=0
%\end{equation}
%
%\subsubsection*{Example of Sub-subheading}
%This is how \cite{Luke1988} produced an unnumbered equation under a
%third level heading.
%\begin{equation}
%  \mathbf J=\sigma(\mathbf E+\mathbf u\times\mathbf B)
%\end{equation}
%\newpage
%

>>>>

\newcommand{\TODO}[1]{\textcolor{blue}{TODO: #1} \\}
\newcommand{\Fede}[1]{\textcolor{green}{Fede: #1} \\}
\newcommand{\Pablo}[1]{#1}
\newcommand{\newf}[1]{#1}
\newcommand{\nof}[1]{\textcolor{cyan}{}}
%\newcommand{\nof}[1]{\textcolor{cyan}{{\sout{#1}}}}

@@

\abstract{
During the last two decades characterization capabilities of porous media have been transformed by advances on computation and visualization technologies.  
It is now possible to obtain a fairly good visualization of the microstructure by computer tomographies. Discrete, diffusion or fluid flow simulations can be run in these domains obtaining traditional experimental characterization parameters. However, the characterization itself has not suffered a significant change because our models have not been updated. On this regard, new models are needed to achieve better up-scaling. A multi-scale approach for up-scaling renders into a model that keeps track of different phenomena happening at different scales and that is coupled in all scales simultaneously imposing great challenges for the solution method. In this work we study the suitability of a high-order least-square method for the solution of a multi-scale transport equation for porous media. Our results show that the method is particularly well suited for the solution of the equation that models 1D transport with reactions 
depending strongly on the scale, even in the presence of a multi-scale coupling term.
}
\keywords{
  Chemical reactions, pore size distribution, LSQ
}
\normalfont\normalsize

@@

\section{Introduction}
Theories for studying porous media were first formulated as early \newf{as }the end of the eighteen century\newf{,} after the volume fraction concept was introduced for describing mud. Half a century later\newf{,} one of the most basic law\newf{s} for saturated porous solids was established by Henry Darcy, i.e. the flow velocity of the liquid in a porous solid is proportional to the pressure gradient. Since then\newf{, increasingly} more complex theories for predicting the proportionality constant \newf{have arised}, incorporating the capillary force and considering deformable media with the definition of the consolidation problem \citep{Boer1992}.

@@

The multi-scale transport equation for porous media (MSTE) was proposed as an extension of approaches considering a finite number of groups \citep{Chen1989, bouffard2001}. One internal coordinate was recently introduced \citep{DupuySchwarz} to the continuity problem for accounting the multi-scale transport of species and the scale-dependent physics. Furthermore, the MSTE defines an inter-pore redistribution function $h$ that makes the equation open and requires further research to find the most adequate closure or model.

@@

\newf{Several numerical methods have been developed for solving integro--differential equations in other areas of science. Examples are the neutron transport equation \cite{Duderstadt1976} and the population balance equation \cite{Ramkrishna2000}. Most of these methods are designed to eliminate the integral terms from the equations.}
\newf{In recent years, the work by \cite{Dorao05a}, \cite{Patruno2010} and \cite{Sporleder2011} has shown the capability of the least-squares method (LSQ) to solve the integro-differential form of the equations directly. This spectral method is based on the idea that under certain conditions minimizing the residual of the equations defined with the numerical solution is equivalent to minimizing the error, i.e., the distance between the numerical solution and the exact solution \cite{Jiang1998}. This reformulation of the equations as a minimization problem is independent of the equations at hand, and therefore it allows for flexible and general--purpose programming. Besides, the method uses a measure of the residual as a built-in error estimator, and presents semi-analytical solutions, as the minimizing function is expanded in a family of basis functions. When combined with the finite or spectral element approach \cite{Gerritsma2010}, it is capable of solving large problems in arbitrary geometries, using unstructured meshes.}

@@

Traditionally, the transport of a given specie with concentration $\phi$ convected by plug flow through a porous media without diffusion in one dimension (z) can be written as:

\begin{equation}
\epsilon v \frac{\phi(z)}{\partial z}=S(z)
\end{equation}

\noindent where $v$ is the advective velocity, $\epsilon$ is the void (or fluid) porosity and the right hand side is a source term. However, this approach is not able to capture all the degrees of freedom present in real porous media and the two-porosity model has been a successful first extension towards a more scale-size-related approach. Recently, a multi-scale approach has been introduced as a generalization to this concept based on the pore scale \cite{DupuySchwarz}.

The term \nof{pore-size have}\newf{pore size has} been used loosely in the literature and needs to be addressed first. \newf{In our framework, it is a characteristic length that represents the pore scale. } Some authors \cite{dullien1991} proposed \nof{to use}\newf{to define the pore size as} twice the hydraulic radius\nof{as a convenient definition but others might work as well in the present approach since what we are after is a characteristic length that will represent the pore scale}. \nof{Any of these choices requires a proper definition of a pore as a unity, for which any arbitrary definition of a portion of the void volume can chosen where a pore size can be measure (e.g. hydraulic radius) for each pore.}\newf{Other definitions may be used. Regardless of the choice, a consitent definition of a pore as a unity is required.} Most pore networks agree on the definition of these elementary units. Each pore will therefore have a volume. In the MSTE, all the void volume is assigned to pores, and the concept of throat \citep{oren2002, blunt2002, piri2005} is not needed\newf{. This is different to} \nof{making a difference with }some pore network strategies.

%\Fede{Lo cambi\'e bastante porque no se entend\'ia, perd\'on. Si falta algo, ponga nom\'as...}
%\Fede{Qu\'e es throat? Pore networks? Capaz alguna ref? Y si estas diferencias con otros m\'etodos establecidos las ponemos en la intro?}

\nof{Let's}\newf{Let us} define $\xi$ as the pore size, and $\epsilon(\xi)d\xi$ \newf{as the total volume of the pores} \nof{the summed volume for all the pores }of sizes between $\xi$ and $\xi+d\xi$ per volume unit.
\nof{On average, the permeability will be different for each pore size as well, $k(\xi)$. A driven force will produce an advective velocity of the fluid at the scale $\xi$ denoted as $v(\xi)$, and the discharge (or slip velocity) for the same scale is $q(\xi)=\epsilon(\xi) v(\xi)$.}
\newf{We will indicate the permeability of a pore of size $\xi$ with $k(\xi)$, the advective velocity of the fluid at the scale $\xi$ as $v(\xi)$, and the discharge (or slip velocity) for the same scale as $q(\xi)=\epsilon(\xi) v(\xi)$}.

% \Fede{De nuevo cambio, pero me pareci\'o que la intenci\'on era definir variables. Igual, no est\'a muy claro. Se nota que no estoy en tema. Pero m\'as all\'a de eso, te puedo preguntar si $\epsilon$ y $q$ son distribuciones o no (hasta ahora no, m\'as adelante s\'i), y a $\phi$ nunca la introduc\'is tampoco (s\'e que es el tracer, pero exactamente c\'omo se define??).}

%\Fede{Capaz podr\'ias empezar definiendo $\phi$ y el problema f\'isico, poner la ecuaci\'on, describir los t\'erminos y las variables que aparecen claramente, y despu\'es las otras como $\epsilon$, que en la ecuaci\'on no figuran directamente... Te va as\'i? Esta secci\'on es cr\'itica, porque el modelo es muy muy poco conocido.}
% \Fede{Dejo de corregir la secci\'on. Me gustar\'ia de ser posible que ac\'a hagas una intro al modelo general, y el 1D introducirlo despu\'es, como simplificaci\'on... }

Recent works \cite{DupuySchwarz} introduced the concept of the redistribution function $h(\xi_1 \rightarrow \xi_2)$ as the discharge from pores of size $\xi_1$ into pores of sizes $\xi_2$. This is a measure of the mixing between pores of different scales.

@@

The multi-scale transport for a tracer in all the pores assuming one dimension ($z$) and steady state case can be written as \citep{DupuySchwarz}:

\begin{align}
q(z, \xi) \cdot \frac{\partial \phi(z, \xi)}{\partial z}  = 
 S(z, \xi) + \int [\phi(z, \hat \xi) - \phi(z, \xi)] h(z, \hat \xi \rightarrow \xi) d\hat \xi . 
\label{eq:ss2}
\end{align}

@@

%\Fede{Te saqu\'e un aporte, no te ofendas :-)}

@@

%\Pablo{Yo lo entiendo porque yo se LSQ (algo al menos)... pero no se como se explica mejor realmente... $\mathbf{f}$ es la solucion o es la aproximacion a la solucion? equacion 2 es inconsistente con el resto... o no? Es una muy poco feliz decision elegir el mismo symbolo para ambas, o no? Debido a que en nuestro problema la solucion es $\phi$ decidi hacer el cambio en la definicion del problema. Luego usamos $\mathbf{f}$ para la aprox solo.  Agregue un texto que capaz ayuda para aclarar ese punto.}
%\Fede{Yo tampoco s\'e c\'omo explicarlo mejor, jeje. Es lo m\'as simplificado que puedo hacerlo, sin mandar fruta for export y sin ir en contra de los fundamentos matem\'aticos. Hice cambios basados en tus comentarios, y creo que ahora queda mejor. Pero sig aceptando sugerencias. No tengo forma f\'acil de explicar el espacio Y. Est\'a definido impl\'icitamente en el problema, es el espacio im\'agen del mapeo que hace el operador. }

@@

%\Pablo{No he leido esta seccion todavia en mucho detalle. Pero parece estar bien. Si es la primera vez que se publica este tipo de informacion decime que agarro la lupa y la miro en mas detalle... se la podes dar a Hugo a ver si la entiende, jeje }
%\Fede{Hugo se duerme en estas secciones. Dice que ya lo conoce, despu\'es me viene a preguntar 3 veces por semana cosas que explico justamente en estas secciones... Tengo un paper aceptado que muestra esto en casi igual :-)}
Using variational analysis, minimizing the functional $\mathcal{J}(\mathbf{f})$ is equivalent to finding $\mathbf{f} \in X(\Omega)$ such that:

@@

%\Fede{Si el problema a resolver ya se introdujo en la segunda secci\'on, entonces esto de ac\'a puede ir a la secci\'on de implementaci\'on :-)}

@@

\begin{align}
\epsilon(\xi)=&A (\xi-\xi_0) (-\xi+\xi_f) \\
q({\xi}) =&V \epsilon(\xi) \xi^2\\
h(\hat \xi, \xi, z) =& q(\hat \xi) q(\xi)/L\\
\phi(\xi, z) =& 10 sin(z) (1-M Log({\xi}/R))\\
\nonumber S(\xi, z)=& 10 A V cos(z) {\xi}^2 ({\xi}-\xi_0) (\xi_f-{\xi}) \left(1-M \text{Log}\left[\nicefrac{{\xi}}{R}\right]\right) +\\
\nonumber  &A^2 M V^2  (360 L)^{-1} {\xi}^2 ({\xi}-\xi_0) ({\xi}-\xi_f) sin(z) \times ... \\
\nonumber  &\big(-81 \xi_0^5+175 \xi_0^4 \xi_f-175 \xi_0 \xi_f^4+  ...\\
\nonumber &81 \xi_f^5+60 \xi_0^4 (3 \xi_0-5 \xi_f) \text{Log}\left[\frac{\xi_0}{{\xi}}\right]+ ...\\
& 60 (5 \xi_0-3 \xi_f) \xi_f^4 \text{Log}\left[\frac{\xi_f}{{\xi}}\right]\big)
\end{align}

\noindent \newf{with $A=\nicefrac{1}{500}~\text{mm}^{-3}$, $V=0.001 \nicefrac{\text{m}}{\text{mm}^2 \text{s}}$, $M=1$, $R=2\xi_f$, $L=10^{-5}~\nicefrac{\text{m}^2}{\text{s}}$ and pore scale limits $\xi_0=1$ mm and $\xi_f=10$ mm.}

@@

For completeness, the condition number versus the order of the approximation is shown in Figure \ref{fig:cond}. This number increases steeply with the order, reaching values over $10^{12}$. The condition number depends mostly on the fill-up of the matrix. The use of an element approach will reduce drastically this number. Larger models that use the MSTE are also expected to have lower condition numbers.

@@

Future work still remains on the area of finding the most adequate kernels that best represent different porous media. Mainly empirical studies of the redistribution function need to be done.
%\Fede{Ahora me tengo que ir, pero hay que mejorar esta conclusi\'on}
%\TODO{Conclusiones en serio?}
%\TODO{Bibliograf\'ia!!}
%\abstract{
%  This file is an example \LaTeX file for submission to CFD2011.  A
%  limit of 10 pages applies.
%}
%\keywords{
%  CFD, hydrodynamics, chemical reactors
%}
%\normalfont\normalsize
%
%
%
%%\section{Nomenclature}
%A complete list of symbols used, with dimensions, is required.
%%the nomenclature needs to be entered into the file ExampleFile.nls
%\printnomenclature[0.7cm]  
%\vskip .1em
%
%
%\section{Introduction}
%The introduction goes here.
%
%
%\newpage
%
%
%
%\section{Model Description}
%You should give a thorough description of your model.
%\vspace{4cm}
%\subsection{Example of Subheading}
%Here is how to produce a numbered equation under a second level
%heading \cite{James1988}.
%\vspace{2cm}\\
%\emph{Continuity equation}
%\begin{equation}
%  \frac{\partial \rho_G}{\partial t}+\nabla\left(\rho_G\mathbf
%    u\right)=0
%\end{equation}
%
%\subsubsection*{Example of Sub-subheading}
%This is how \cite{Luke1988} produced an unnumbered equation under a
%third level heading.
%\begin{equation}
%  \mathbf J=\sigma(\mathbf E+\mathbf u\times\mathbf B)
%\end{equation}
%\newpage
%
